### 2014-03-08 src/analysis.Rnw
update

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

>>>>

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

### 2014-03-08 src/methodology.Rnw
update

<<opstable,results='asis'>>=
op=c(
'INVERT-NEGS',
'RETURN-VALS',
'MATH',
'VOID-M-CALLS',
'NEGATE-COND',
'COND-BOUNDARY',
'INCREMENTS',
'NVOID-M-CALLS',
'CONSTR-CALLS',
'INLINE-CONSTS',
'RM-INCR',
'E-MEMBER-VAR',
'E-SWITCH',
'RM-SWITCH',
'RM-COND',
'DELETE-COND')
expl=c(
'Invert negatives',
'Change return values',
'Modify arithmetic operators',
'Remove void method calls',
'Negate conditional statements',
'Modify boundary conditions',
'Modify increment/decrement',
'Replace non-void method calls',
'Replace constructor calls',
'Replace inline constants',
'Remove increment/decrement',
'Replace member variable assignments',
'Modify switch statements',
'Remove switch elements*',
'Make conditionas true',
'Make conditionas false*')
op.df <- data.frame(Operator=op, Explanation=expl)
print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='tbl:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
@

>>>>

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false*
\end{tabular}
\caption{PIT Mutation Opeators}
\label{tbl:pitop}
\end{table}
